Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
intro sections

Nowadays, many cloud vendors have started offering virtual machines (VM) with GPUs in order to provide
GPGPU computation service to users who need it. An examples of that are:
Amazon Web Services (AWS), Penguin Computing, Softlayer and Microsoft Azure.
In the pubic scope, one of the most popular cloud vendors is AWS that has a wide range of preconfigured instances ready to be launched.
Otherwise, owning the propper infrastructure, a private cloud can be deployed using a specific middleware such as
Openstack or Opennebula.

@@

>>>>

Nowadays, many cloud vendors have started offering virtual machines (VM) with GPUs in order to provide
GPGPU computation service to users who need it. An examples of that are:
Amazon Web Services (AWS), Penguin Computing, Softlayer and Microsoft Azure.
In the public scope, one of the most popular cloud vendors is AWS that has a wide range of preconfigured instances ready to be launched.
Otherwise, owning the propper infrastructure, a private cloud can be deployed using a specific middleware such as
Openstack or Opennebula.

@@

The rest of the paper is structured as follows: 
in Section~\ref{sec:background} the technologies used are explained;
Section~\ref{sec:state} summarizes previous work in this field; 
Section~\ref{sec:motivation} states the motivation to carry out this work;
all the effort made using AWS is explained in Section~\ref{sec:workingaws};
while the effort made in Openstack is described in Section~\ref{sec:openstack};
finally Section~\ref{sec:conclusions} gives an overview of the advances made and~\ref{sec:future} propose the next steps
should be take in this research.
